### 2013-12-23 thesis/src/appendices/listings.tex
Supply test case description with a figure and table of average deployment time for C-SAP
New deployment time figure

\section{Service specifications}
\lstinputlisting[caption=Cloud-SAP Service Specification (without scaling policies), label=lst:service-spec-test-cost]{appendices/service-spec-test-cost.json}

>>>>

\section{Service specifications}
\lstinputlisting[caption=Carina Environment Specification which was used during tests of deployment time, label=lst:carina-config]{appendices/carina-svc-config.rb}

\lstinputlisting[caption=Cloud-SAP Service Specification (without scaling policies), label=lst:service-spec-test-cost]{appendices/service-spec-test-cost.json}

\lstinputlisting[caption=Cloud-SAP Service Specification used for testing deployment time, label=lst:service-spec-test-deployment-time]{appendices/service-spec-deployment-time-test.json}

### 2013-12-23 thesis/src/chapters/chapter-7-evaluation.tex
Thesis: Changed sap-layers drawing, moved requirements to an implementation section
New deployment time figure

\section{Deployment time -- solution comparison}
\subsection{Motivation}
In this test we want to compare our solution to one of those available at the market which use \emph{OpenNebula} as an underlying tool for managing resources of a data center and \emph{OpenVZ} as a hypervisor in terms of \textbf{deployment time}, one of the most important factors of products whose main purpose is to scale applications.
\emph{Carina} \cite{Carina} can be considered a perfect match of a solution for such a comparison and tests are ran against it.
\subsection{Description and preconditions}
This test involves the steps of
  \begin{inparaenum}[i)]
    \item instantiating one of the tested product, i.e. Cloud-SAP or Carina,
    \item ordering the deployment of a service whose specification is shown in listing \ref{lst:service-spec-test-deployment-time},
    \item measuring the time needed to set up the environment of the service.
  \end{inparaenum}
Before performing any tests all virtual machines present at the deployment node are removed.
\subsubsection{Service description}
The service comprises a simple java enterprise application, deployed in a master-slave configuration with one VM set as a load balancer and other nodes that serve as workers, which uses Tomcat as a web container.

@@

\begin{table}
  \centering
  \begin{tabular}{ c  c  c }
    \hline
    & \multicolumn{2}{c}{Solution} \\
    \cline{2-3}
    Instance no & Cloud-SAP & Carina \\
    \hline
    2 & 103.9s & x \\
    3 & 166.3s & x \\
    4 & 225.5s & x \\
    5 & 288.3s & x \\
    \hline
  \end{tabular}
  \caption{Average deployment time for the service with the various number of VMs used for the whole environment}
  \label{tbl:test-service-deployment-time}
\end{table}

>>>>

\section{Deployment time -- solution comparison}
\subsection{Motivation}
In this test we want to compare our solution to one of those available at the market which use \emph{OpenNebula} as an underlying tool for managing resources of a data center and \emph{OpenVZ} as a hypervisor in terms of \textbf{deployment time}, one of the most important factors of products whose main purpose is to scale applications.
\emph{Carina} \cite{Carina} can be considered a perfect match of a solution for such a comparison and tests are ran against it.
\subsection{Description and preconditions}
This test involves the steps of
  \begin{inparaenum}[i)]
    \item instantiating one of the tested product, i.e. Cloud-SAP or Carina,
    \item ordering the deployment of a service whose specification is shown in listing \ref{lst:service-spec-test-deployment-time},
    \item measuring the time needed to set up the environment of the service.
  \end{inparaenum}
Before performing any tests all virtual machines present at the deployment node are removed.
\subsubsection{OpenNebula configuration}
To ensure objectivity in tests, OpenNebula was configured in both products in the same way. One of the key factors that could influence the deployment time is the configuration of scheduler. Its parameters are shown in the listing \ref{lst:one-scheduler-config}.
\lstinputlisting[caption=OpenNebula scheduler configuration, label=lst:one-scheduler-config]{deployment-time-test-sched-config}
\subsubsection{Service description}
The service comprises a simple java enterprise application, deployed in a master-slave configuration with one VM set as a load balancer and other nodes that serve as workers, which uses Tomcat as a web container.

The description of a service expressed in Carina format can be found in listing \ref{lst:carina-config}.

@@

\begin{table}
  \centering
  \begin{tabular}{ c  c  c }
    \hline
    & \multicolumn{2}{c}{Solution} \\
    \cline{2-3}
    Instance no & Cloud-SAP & Carina \\
    \hline
    2 & 198.0 & 158.7s \\
    3 & 261.72 & 208.1s \\
    4 & 294.38 & 230.6s \\
    \hline
  \end{tabular}
  \caption{Average deployment time for the service with the various number of VMs used for the whole environment}
  \label{tbl:test-service-deployment-time}
\end{table}
